Informing policy via dynamic models: Cholera in Haiti

### 2023-08-23 ms-plos.Rnw
Updated SI w/ haitipkg, minor edits

%%%% parameters %%%%%%%%%%%
\newcommand\Wsat{W_{\mathrm{sat}}}
\newcommand\muIR{\mu_{IR}}
\newcommand\muEI{\mu_{EI}}
\newcommand\transmission{\beta}
\newcommand\seasAmplitude{a}
\newcommand\rainfallExponent{r}
\newcommand\muRS{\mu_{RS}}
\newcommand\vaccineEfficacy{\vartheta}
\newcommand\muBirth{\mu_S}
\newcommand\muDeath{\delta}
\newcommand\choleraDeath{\delta_{C}}
\newcommand\symptomFrac{f}
\newcommand\asymptomRelativeInfect{\epsilon}
\newcommand\asymptomRelativeShed{\epsilon_{W}}
\newcommand\Wbeta[1]{\beta_{W#1}}
\newcommand\Whur[1]{\beta_{W#1}^{hm}}
\newcommand\hHur[1]{h_{#1}^{hm}}
\newcommand\tHur{t_{hm}}
\newcommand\Wremoval{\delta_W}
\newcommand\Wshed{\mu_W}
\newcommand\mixExponent{\nu}
\newcommand\sigmaProc{\sigma_{\mathrm{proc}}}
\newcommand\reportRate{\rho}
\newcommand\obsOverdispersion{\psi}
\newcommand\phaseParm{\phi}
\newcommand\transmissionTrend{\zeta}
\newcommand\Binit{\xi}
\newcommand\vaccClass{Z}
\newcommand\vaccCounter{z}
\newcommand\modelCounter{m}
\newcommand\missing{---}
\newcommand\fixed{\color{blue}}
\newcommand\demography{\bullet}
\newcommand\code[1]{\texttt{#1}}
\newcommand\figTitle{\bf}
\newcommand\paramVec{\theta}
\newcommand\childReduce{q}

@@

# Just a bit of tidying up: removing parameters that we won't use again.
rm(
  SEARCH1, SEARCH2, SEARCH3, N_SEARCHES,
  est_param_names, est_param_names_expanded,
  set_rw_1, set_rw_2, set_rw_3, reg_rw_1.sd, reg_rw_2.sd, reg_rw_3.sd,
  chol_rw_1.sd, chol_rw_2.sd, chol_rw_3.sd
)
gc()

@@

\multirow{2}{*}{Initial Values} & $I_{0,0} = \Sexpr{round(prod(p1[c('pop_0', 'I_0')]))}$

@@

  & \multirow{2}{*}{$I_{3,7,10;0}(0)= (
        \Sexpr{round(prod(p3[c('H3', 'Iinit3')]))}, \Sexpr{round(prod(p3[c('H7', 'Iinit7')]))}, \Sexpr{round(prod(p3[c('H10', 'Iinit10')]))})^*$}

>>>>

%%%% parameters %%%%%%%%%%%
\newcommand\Wsat{W_{\mathrm{sat}}}
\newcommand\muIR{\mu_{IR}}
\newcommand\muEI{\mu_{EI}}
\newcommand\transmission{\beta}
\newcommand\seasAmplitude{a}
\newcommand\rainfallExponent{r}
\newcommand\muRS{\mu_{RS}}
\newcommand\vaccineEfficacy{\vartheta}
\newcommand\muBirth{\mu_S}
\newcommand\muDeath{\delta}
\newcommand\choleraDeath{\delta_{C}}
\newcommand\symptomFrac{f}
\newcommand\asymptomRelativeInfect{\epsilon}
\newcommand\asymptomRelativeShed{\epsilon_{W}}
\newcommand\Wbeta[1]{\beta_{W#1}}
\newcommand\Whur[1]{\beta_{W#1}^{hm}}
\newcommand\hHur[1]{h_{#1}^{hm}}
\newcommand\tHur{t_{hm}}
\newcommand\Iinit{I_{0,0}}
\newcommand\Einit{E_{0, 0}}
\newcommand\Wremoval{\delta_W}
\newcommand\Wshed{\mu_W}
\newcommand\mixExponent{\nu}
\newcommand\sigmaProc{\sigma_{\mathrm{proc}}}
\newcommand\reportRate{\rho}
\newcommand\obsOverdispersion{\psi}
\newcommand\phaseParm{\phi}
\newcommand\transmissionTrend{\zeta}
\newcommand\Binit{\xi}
\newcommand\vaccClass{Z}
\newcommand\vaccCounter{z}
\newcommand\modelCounter{m}
\newcommand\missing{---}
\newcommand\fixed{\color{blue}}
\newcommand\demography{\bullet}
\newcommand\code[1]{\texttt{#1}}
\newcommand\figTitle{\bf}
\newcommand\paramVec{\theta}
\newcommand\childReduce{q}

@@

# Just a bit of tidying up: removing parameters that we won't use again.
rm(
  SEARCH1, SEARCH2, N_SEARCHES,
  est_param_names, est_param_names_expanded,
  set_rw_1, set_rw_2, set_rw_3, reg_rw_1.sd, reg_rw_2.sd, reg_rw_3.sd,
  chol_rw_1.sd, chol_rw_2.sd, chol_rw_3.sd
)
gc()

@@

\multirow{2}{*}{Initial Values} & $\Iinit = \Sexpr{round(prod(p1[c('pop_0', 'I_0')]))}$

@@

  & \multirow{2}{*}{$\Iinit^{3,7,10} = (
        \Sexpr{round(prod(p3[c('H3', 'Iinit3')]))}, \Sexpr{round(prod(p3[c('H7', 'Iinit7')]))}, \Sexpr{round(prod(p3[c('H10', 'Iinit10')]))})^*$} % TODO: Check the unit numbers
